\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-09-19 write_up/cricket.tex
fixed intro + minor correction for readme

But before we move to seriously consider these solutions, we may ask about the evidence.

\citep{de1998winning}, \citep{dawson2009bat}, \citep{Weintraub2010}, \citep{Saad2015}

>>>>

To assess the net observed advantage of winning the toss, we leverage data from over 43,000 first-class men's cricket matches --- to our knowledge, largest ever dataset assembled for the question, and nearly 50--100 times larger than used in prominent previous attempts \citep[see,][]{dawson2009bat, de1998winning}. Using the data, we estimate the impact of winning the toss on the probability of winning a match. Unlike some other studies on the topic, e.g. \citet{dawson2009bat, Saad2015}, we do not condition on post coin-toss decisions to avoid post-treatment bias \citep[see][]{acharya2015}. We find that winning the toss grants a small but significant advantage, but that advantage varies considerably and systematically.
